---
title: "units2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
```

units2 is a simple (and probably temporary) wrapper to the units class provided by the [units](https://github.com/edzer/units) package. Specifically, it avoids non-standard evaluation and the silent creation of unitless units, as was needed for my programmatic and piping needs.

### Parse unit from string

#### String formats

`units::parse_unit` only supports product power form (e.g. `"kg m2 s-1"`). `units2::parse_unit` supports product power form (including `"+"`), arithmetic expressions (e.g. `"kg * (m^2 / s)"`), and any combination thereof (e.g. `"kg+1 (m^2 s-1)"`).
  
```{r}
units2::parse_unit("kg m2 s-1")
units2::parse_unit("kg (m^2 / s)")
units2::parse_unit("kg+1 (m^2 s-1)")
units2::parse_unit("in/s")
units2::parse_unit("°")

```
  
#### Unit names with numbers

`units::parse_unit` fails with units with numbers in their name. `units2::parse_unit` fixes this.
  
```{r}
unit_names <- names(units::ud_units)
unit_names[grepl("[0-9]", unit_names)]
```
  
```{r}
tryCatch(units::parse_unit("H2O"), error = function(e) print(e))
```
```{r}
units2::parse_unit("H2O")
units2::parse_unit("H2O1")
units2::parse_unit("1 / H2O-1")
```

#### Unknown units

`units::parse_unit` silently creates new units. `units2::parse_unit` throws an error.

```{r}
units::parse_unit("unknown")
tryCatch(units2::parse_unit("unknown"), error = function(e) print(e))
```

#### Unit symbols

As a side effect of evaluating the constructed expression against `units::ud_units`, `units2::parse_unit` always replaces unit names with their corresponding symbols.

```{r}
units::parse_unit("meters seconds-1")
units2::parse_unit("meters seconds-1")
```

### Deparse unit to string

`units::as_cf` is renamed `units2::deparse_unit` for symmetry with `parse_unit`.
  
### Coercion and conversion

`units2::as_units` and `units2::convert_units` accept either string or units objects as unit specifications, while `units::as.units` and `units::set_units` accepts only the latter.

```{r}
library(magrittr)
x <- 1:10
from <- "meters s-1"
to <- "km hour-1"
# units
x %>%
  units::as.units(value = units::parse_unit(from)) %>%
  units::set_units(value = units::parse_unit(to))
# units2 equivalent
x %>%
  units2::convert_units(from = from, to = to)
```

`units2` drops support for the non-standard evaluation in `units::set_units` because `units2::parse_unit` supports that notation in string form, avoiding confusing behavior:

```{r}
units2::as_units(x, "meters/s")
tryCatch(units::set_units(x, meters/s), error = function(e) print(e))
meters <- 0.01
tryCatch(units::set_units(x, meters/s), error = function(e) print(e))
```
